### 2024-06-05 Scripts/Manuscript_scripts.Rmd
Update Manuscript_scripts.Rmd

@@

>>>>

chordDiagram(uniqueVar[, c('predictor_reformat', 'item', 'p_adjusted_log')], 
             order = ord, 
             annotationTrack = "grid", 
             link.sort = TRUE,
             grid.col = grid.col, 
             col = col_fun$col, 
             transparency = 0,
             annotationTrackHeight = mm_h(2),
             preAllocateTracks = list(track.height = 0.3))

circos.track(track.index = 1,
             panel.fun = function(x, y) {
               circos.text(CELL_META$xcenter, CELL_META$ylim[2] - 0.92,  # Adjust the + 0.15 to move the text more outwards if required
                           CELL_META$sector.index, 
                           facing = "clockwise", 
                           niceFacing = TRUE, 
                           adj = c(0, 0.5), 
                           cex = 1.0)
             }, bg.border = NA)

@@

```{r Fig 4a}

df_statistics <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\mobile_elements_finder-category_statistics+sem.csv)')
df_statistics['MGE_per_genome_round'] <- round(df_statistics['MGE_per_genome'],2)

limits <- aes(ymax = MGE_per_genome+standard_error,
              ymin = ifelse(MGE_per_genome-standard_error<0,0,MGE_per_genome-standard_error))

df_statistics_acinetobacter <- subset(df_statistics,species=='acinetobacter')
p_acinetobacter <- ggplot(df_statistics_acinetobacter, aes(x=mge_type, y=MGE_per_genome)) + 
  geom_errorbar(limits, width=.2,col='#d08b70',
                position=position_dodge(.9)) +
  geom_bar(stat = "identity",fill='#d08b70') + 
  # geom_text(aes(label=MGE_per_genome_round),position=position_dodge(width=0.9), vjust=-0.25) + 
  scale_x_discrete(limits=c('insertion sequence','unit transposon','composite transposon','mite','ice')) +
  ylim2(limits = c(0,10)) + xlab(NULL) + ylab(NULL) + labs(title = 'A. baumannii') +
  theme_bw()  +
  theme(axis.text.x  = element_blank(),axis.text.y = element_text(size=36),axis.ticks.x = element_blank()) + 
  theme(strip.background = element_blank(),
        plot.title  = element_textbox(
          size = 34,
          color = "#4d4d4d", fill = "#dbdad9", box.color = "black",face = 'italic',
          halign = 0.5, linetype = 1,  width = unit(1, "npc"),
          margin = margin(0, 0, 0, 0),padding = margin(6, 6, 6, 6)),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

df_statistics_corynebacterium <- subset(df_statistics,species=='corynebacterium')
p_corynebacterium <- ggplot(df_statistics_corynebacterium, aes(x=mge_type, y=MGE_per_genome)) + 
  geom_errorbar(limits, width=.2,col='#988b74',
                position=position_dodge(.9)) +
  geom_bar(stat = "identity",fill='#988b74') + 
  # geom_text(aes(label=MGE_per_genome_round),position=position_dodge(width=0.9), vjust=-0.25) + 
  scale_x_discrete(limits=c('insertion sequence','unit transposon','composite transposon','mite','ice')) +
  ylim2(limits = c(0,10)) + xlab(NULL) + ylab(NULL) + labs(title = 'C. striatum') +
  theme_bw()  +
  theme(axis.text.x  = element_blank(),axis.ticks.x = element_blank(),axis.ticks.y =element_blank(), axis.text.y =element_blank()) +
  theme(strip.background = element_blank(),
        plot.title  = element_textbox(
          size = 34,
          color = "#4d4d4d", fill = "#dbdad9", box.color = "black",face = 'italic',
          halign = 0.5, linetype = 1,  width = unit(1, "npc"),
          margin = margin(0, 0, 0, 0),padding = margin(6, 6, 6, 6)),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

df_statistics_klebsiella <- subset(df_statistics,species=='klebsiella')
p_klebsiella <- ggplot(df_statistics_klebsiella, aes(x=mge_type, y=MGE_per_genome)) + 
  geom_errorbar(limits, width=.2,col='#6fa9c8',
                position=position_dodge(.9)) +
  geom_bar(stat = "identity",fill='#6fa9c8') + 
  # geom_text(aes(label=MGE_per_genome_round),position=position_dodge(width=0.9), vjust=-0.25) + 
  scale_x_discrete(limits=c('insertion sequence','unit transposon','composite transposon','mite','ice')) +
  ylim2(limits = c(0,10)) + xlab(NULL) + ylab(NULL) + labs(title = 'K. pneumoniae') +
  theme_bw()  +
  theme(axis.text.x  = element_blank(),axis.ticks.x = element_blank(),axis.ticks.y =element_blank(), axis.text.y =element_blank()) +
  theme(strip.background = element_blank(),
        plot.title  = element_textbox(
          size = 34,
          color = "#4d4d4d", fill = "#dbdad9", box.color = "black",face = 'italic',
          halign = 0.5, linetype = 1,  width = unit(1, "npc"),
          margin = margin(0, 0, 0, 0),padding = margin(6, 6, 6, 6)),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

df_statistics_pseudomonas <- subset(df_statistics,species=='pseudomonas')
p_pseudomonas <- ggplot(df_statistics_pseudomonas, aes(x=mge_type, y=MGE_per_genome)) + 
  geom_errorbar(limits, width=.2,col='#98c5b4',
                position=position_dodge(.9)) +
  geom_bar(stat = "identity",fill='#98c5b4') + 
  # geom_text(aes(label=MGE_per_genome_round),position=position_dodge(width=0.9), vjust=-0.25) + 
  scale_x_discrete(limits=c('insertion sequence','unit transposon','composite transposon','mite','ice'),
                   labels=c('IS','Unit Transposon','Composite Transposon','MITE', 'ICE')) +
  ylim2(limits = c(0,10)) + xlab(NULL) + ylab('Number of mobile elements\nper genome') + labs(title = 'P. aeruginosa') +
  theme_bw()  + 
  theme(strip.background = element_blank(),
        plot.title  = element_textbox(
          size = 34,
          color = "#4d4d4d", fill = "#dbdad9", box.color = "black",face = 'italic',
          halign = 0.5, linetype = 1,  width = unit(1, "npc"),
          margin = margin(0, 0, 0, 0),padding = margin(6, 6, 6, 6)),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) + 
  theme(axis.text.x = element_text(angle = 30,hjust = 1,size=30),
        axis.text.y = element_text(size = 36),
        axis.title.y = element_text(size=36)) #change ylabs fontsize,ylab() --> axis.title.y()

df_statistics_stenotrophomonas <- subset(df_statistics,species=='stenotrophomonas')
p_stenotrophomonas <- ggplot(df_statistics_stenotrophomonas, aes(x=mge_type, y=MGE_per_genome)) + 
  geom_errorbar(limits, width=.2,col='#384073',
                position=position_dodge(.9)) +
  geom_bar(stat = "identity",fill='#384073') + 
  # geom_text(aes(label=MGE_per_genome_round),position=position_dodge(width=0.9), vjust=-0.25) + 
  scale_x_discrete(limits=c('insertion sequence','unit transposon','composite transposon','mite','ice'),
                   labels=c('IS','Unit Transposon','Composite Transposon','MITE', 'ICE')) +
  ylim2(limits = c(0,10)) + xlab('Mobile element type') + ylab(NULL) + labs(title = 'S. maltophilia') +
  theme_bw()  +
  theme(axis.ticks.y =element_blank(), axis.text.y =element_blank(),axis.text.x = element_text(angle = 30,hjust = 1,size=30)) +
  theme(strip.background = element_blank(),
        plot.title  = element_textbox(
          size = 34,
          color = "#4d4d4d", fill = "#dbdad9", box.color = "black",face = 'italic',
          halign = 0.5, linetype = 1,  width = unit(1, "npc"),
          margin = margin(0, 0, 0, 0),padding = margin(6, 6, 6, 6)),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(size=36)) # change xlabs fontsize, xlab() --> axis.title.x()

df_statistics_EMHOS <- subset(df_statistics,species=='EHMOS')
p_EMHOS <- ggplot(df_statistics_EMHOS, aes(x=mge_type, y=MGE_per_genome)) +
  geom_errorbar(limits, width=.2,col='#b54030',
                position=position_dodge(.9)) +
  geom_bar(stat = "identity",fill='#b54030') + 
  # geom_text(aes(label=MGE_per_genome_round),position=position_dodge(width=0.9), vjust=-0.25) + 
  scale_x_discrete(limits=c('insertion sequence','unit transposon','composite transposon','mite','ice'),
                   labels=c('IS','Unit Transposon','Composite Transposon','MITE', 'ICE')) +
  ylim2(limits = c(0,10)) + xlab(NULL) + ylab(NULL) + labs(title = 'EHMOS') +
  theme_bw()  +
  theme(axis.ticks.y =element_blank(), axis.text.y =element_blank(),axis.text.x = element_text(angle = 30,hjust = 1,size=30)) +
  theme(strip.background = element_blank(),
        plot.title  = element_textbox(
          size = 34,
          color = "#4d4d4d", fill = "#dbdad9", box.color = "black",face = 'italic',
          halign = 0.5, linetype = 1,  width = unit(1, "npc"),
          margin = margin(0, 0, 0, 0),padding = margin(6, 6, 6, 6)),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

p_combined <- plot_list( p_acinetobacter, p_corynebacterium, p_klebsiella,p_pseudomonas,p_stenotrophomonas,p_EMHOS)
p_combined

```{r Fig 4b}

df_mge_abundance = read.csv(r"(\mobile_elements_finder-stats_comparisons-mge_abundance.csv)")
df_mge_abundance$species <- factor(df_mge_abundance$species,levels = c('EHMOS','corynebacterium','stenotrophomonas','pseudomonas','acinetobacter','klebsiella'))
my_comparisons <- list(c('EHMOS','corynebacterium'),c('EHMOS','stenotrophomonas'),c('EHMOS','pseudomonas'),
                       c('EHMOS','acinetobacter'),c('EHMOS','klebsiella'))

ggboxplot(df_mge_abundance, x="species", y="mge_num",
          color = "species", palette =c("#E41A1C","#377EB8","#4DAF4A","#984EA3","#FF7F00","#F781BF","#A65628","#F781BF"),
          add = "jitter",add.params = list(size = 1.5, alpha = 0.5))  +
  stat_boxplot(mapping = aes(color=species),geom = "errorbar",width=0.1)  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=8,
                     vjust=.15,tip.length= c(0,0,0)) + 
  scale_x_discrete(labels=c('EHMOS','C. striatum','S. maltophilia','P. aeruginosa','A. baumannii','K. pneumoniae'))+
  labs(x=NULL,y='Number of mobile elements',) +  
  theme_pubr(base_size = 24,legend ='none',x.text.angle = 30)

```{r Fig 4c}

df_profile <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\mobile_elements_finder-profile.csv)')
df_profile <- subset(df_profile,species !='assembled_contigs_all')

# reorder the species column
df_profile$species <- factor(df_profile$species, levels=c("acinetobacter", "corynebacterium", "klebsiella","pseudomonas","stenotrophomonas","EHMOS"))
# change the facted plots labels
species.labs <- c("A. baumannii", "C. striatum", "K. pneumoniae", "P. aeruginosa", "S. maltophilia", "EHMOS")
names(species.labs) <- c("acinetobacter", "corynebacterium", "klebsiella","pseudomonas","stenotrophomonas","EHMOS")

p_profile <- ggplot(df_profile, aes(x=allele_len,fill=species)) + 
  geom_histogram(color="#e9ecef", alpha=1, position = 'identity') + 
  scale_x_log10(limits=c(100,100000),labels=scales::comma) + ylim2(limits = c(-1,40)) + 
  scale_fill_manual(values = c("acinetobacter"="#d08b70", "corynebacterium"='#988b74', "klebsiella"='#6fa9c8',
                               "pseudomonas"='#98c5b4',"stenotrophomonas"='#384073',"EHMOS"='#b54030')) +
  theme_bw() + 
  facet_grid(species ~ .,
             labeller = labeller(species = species.labs)) +
  xlab('Element length(bp)') + ylab('Number of mobile elements') +
  theme(axis.text.x  = element_text(size = 30),axis.text.y = element_text(size = 30),
        axis.title.x = element_text(size = 32),axis.title.y = element_text(size = 32)) +
  theme(strip.background = element_blank(),
        strip.text.y = element_textbox_simple(size = 22, # left y-label fontsize
                                              color = "#4d4d4d", fill = "#dbdad9", box.color = "black",face = 'italic', orientation = "right-rotated",
                                              halign = 0.5, linetype = 1,  width = unit(1, "npc"),
                                              margin = margin(0, 0, 0, 0),padding = margin(6, 6, 6, 6)),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = 'none',panel.spacing.y = unit(2, "lines"))
p_profile

### claculate the p-values using Kolmogorov-Smirnov Test

vec <- c('pseudomonas','acinetobacter','klebsiella','corynebacterium','stenotrophomonas','EHMOS')

# Generate all pairs
pairs <- combn(vec, 2)

# Convert to a list of vectors, which can be used in stat_compare_means
comparison_list <- split(pairs, col(pairs))

# Conduct KS test for each pair
result_list <- lapply(comparison_list, function(pair) {
  group1 <- df_profile[df_profile$species == pair[1], "allele_len"]
  group2 <- df_profile[df_profile$species == pair[2], "allele_len"]
  ks_result <- ks.test(group1, group2)

  # Return a data frame
  data.frame(
    group1 = pair[1],
    group2 = pair[2],
    p_value = ks_result$p.value
  )
})

# Combine all results into one data frame
result_df <- do.call(rbind, result_list)

# r$> result_df
#              group1           group2      p_value
# 1       pseudomonas    acinetobacter 1.486184e-03
# 2       pseudomonas       klebsiella 2.595425e-03
# 3       pseudomonas  corynebacterium 3.880953e-02
# 4       pseudomonas stenotrophomonas 2.400837e-01
# 5       pseudomonas            EHMOS 6.234450e-05
# 6     acinetobacter       klebsiella 4.514242e-03
# 7     acinetobacter  corynebacterium 3.178381e-08
# 8     acinetobacter stenotrophomonas 7.544480e-02
# 9     acinetobacter            EHMOS 8.663095e-04
# 10       klebsiella  corynebacterium 2.106382e-03
# 11       klebsiella stenotrophomonas 1.432543e-01
# 12       klebsiella            EHMOS 8.003375e-03
# 13  corynebacterium stenotrophomonas 3.150332e-02
# 14  corynebacterium            EHMOS 1.700597e-03
# 15 stenotrophomonas            EHMOS 1.631064e-02

```{r Fig 4d}

# Sample dataset
nodes <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\mobile_elements_finder-draft_genomes-arg_sankey-nodes.csv)',header = F)
names(nodes) <- c('name')
links <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\mobile_elements_finder-draft_genomes-arg_sankey-links-scaled.csv)')

# Create Sankey plot using plotly
p <-plot_ly(type = "sankey",
        domain = list(
          x = c(0, 1),
          y = c(0, 1)
        ),
        orientation = "h",
        valueformat = ".0f",
        node = list(
          pad = 0,
          thickness = 20,
          line = list(
            color = "black",
            width = 0.5
          ),
          label = nodes$name
        ),
        link = list(
          source = links$source,
          target = links$target,
          value = links$normalized_value,
          color = c("rgba(204, 204, 204, 0.35)")
        ),
        width =1500,height =700) %>%
  layout(
    title = NULL,
    font = list(size = 32,family="Arial"),
    xaxis = list(showgrid = FALSE, zeroline = FALSE),
    yaxis = list(showgrid = FALSE, zeroline = FALSE)
  )

```{r Fig 4f}

### Custom function to generate the desired format of the matrix
###-------------------------------------------------------
#Get lower triangle of the correlation matrix
get_lower_tri<-function(cormat){
  cormat[upper.tri(cormat,diag = T)] <- NA
  return(cormat)
}
#Get upper triangle of the correlation matrix
get_upper_tri <- function(cormat){
  cormat[lower.tri(cormat,diag = T)]<- NA
  return(cormat)
}
###-------------------------------------------------------

df_plasmids_ani <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\plasmids_selected-ANI-NZ_CP010782.1_fraglen.csv)")

#replace patient name with patientID
df_plasmids_ani$query <- str_replace(df_plasmids_ani$query,'zhujianfen-zheyi','Patient_6')
colnames(df_plasmids_ani) <-  str_replace(colnames(df_plasmids_ani),'zhujianfen.zheyi','Patient_6')
#remove suffix: '.fasta' 
colnames(df_plasmids_ani) <- str_remove(colnames(df_plasmids_ani),'.fasta')
row.names(df_plasmids_ani) <- str_remove(df_plasmids_ani$query,'.fasta')

#dataframe --> martix
df_plasmids_ani <- df_plasmids_ani[,-1]
matrix_plasmids_ani <- as.matrix(df_plasmids_ani)

#Remeber not to modify the order of samples name, just copy the output of 'table(df$var1)' and 'table(df$var2)' !!!
x_axis<-c("NZ_CP010782.1",
          "NZ_CP008708.1",
          "NZ_CP008850.1",
          "NZ_CP020576.1",
          "NZ_CP030084.1",
          "NZ_CP050414.1",
          "NZ_CP066231.1")
y_axis<-rev(c("NZ_CP008708.1",
              "NZ_CP008850.1",
              "NZ_CP020576.1",
              "NZ_CP030084.1",
              "NZ_CP050414.1",
              "NZ_CP066231.1",
              "Patient_6"))

#reshape data: 'wide' --> 'long'
df <- melt(get_lower_tri(matrix_plasmids_ani),na.rm = T)
colnames(df) <- c('var1','var2','ANI')

#generate the order of "x_axis" and "y_axis"
table(df$var1) 
table(df$var2)

#custom the order so that the plot will display in a lower-left layout
df<-df %>%
  mutate(var1=factor(var1,levels = y_axis),
         var2=factor(var2,levels = x_axis))

#labels to display on the heatmap
txt.df<-data.frame(x=1:8,
                   y=8:1,
                   label=c(
                     "NZ_CP010782.1",
                     "NZ_CP008708.1",
                     "NZ_CP008850.1",
                     "NZ_CP020576.1",
                     "NZ_CP030084.1",
                     "NZ_CP050414.1",
                     "NZ_CP066231.1",
                     'Patient_6'))

df$ANI <- round(df$ANI,3)
p1 <- ggplot(data=df,aes(x=var2,y=var1))+
  geom_tile(aes(fill=ANI),
            color="black", width = 0.92, height = 0.92)+
  geom_text(aes(label=ANI),size=10) +
  geom_text(data=txt.df,
            aes(x=x,y=y,label=label),size=10,
            nudge_x = 0.45,nudge_y = -0.2)+
  scale_fill_gradient2(low = "#fcbcce",mid = '#f2f2f2',high = "#6cb7d5",midpoint = 99.95) +
  theme_bw()+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        legend.position = "right",
        legend.title = element_text(size = 24),
        legend.text = element_text(size = 24),
        axis.title = element_blank())+
  coord_cartesian(xlim = c(0,8),y=c(0,8)) +
  guides(fill=guide_colorbar(barheight = 10,
                             ticks.colour = "black"))

```{r Fig 4g}

bbone <- read_mauve_backbone(r'(E:\learning materials\graduate student\Lab-Data\Task-01-New\Processed-Data\MGEs\PLSDB\mauve_alignment\plasmids_publish_selected.backbone)',
                             ref=1, filter_low=0)
names <- c('NZ_CP010782.1',
           'Patient_6')
names(bbone$dna_segs) <- names

#Calculating the lengths by adding the length on both sides of the comparisons
for (i in 1:length(bbone$comparisons)){
  cmp <- bbone$comparisons[[i]]
  bbone$comparisons[[i]]$length <-
    abs(cmp$end1 - cmp$start1) + abs(cmp$end2 - cmp$start2)
}
plot_gene_map(dna_segs=bbone$dna_segs, 
              comparisons=bbone$comparisons,dna_seg_label_col = "black",
              global_color_scheme=c("length", "auto", "blue_red",0.9),
              override_color_schemes=TRUE)

```{r Fig s4a}

# matrix_rgi_species_all_norm <- normalize(matrix_rgi_species_all,margin = 1,method = 'range',range = c(0,2))
matrix_rgi_species_all_norm <- normalize(matrix_rgi_species_all,margin = 1,method = 'scale')
colnames(matrix_rgi_species_all_norm) <- colnames(matrix_rgi_species_all)

plot_heatmap_species_all <- Heatmap(matrix_rgi_species_all_norm,
                                    #breaks = c(0,1,3),
                                    col = c('#ffffff','#ff0000'),
                                    # col = c('#f7faff','#08306b'),
                                    left_annotation  = rowAnnotation(df=labels_annotation_col,
                                                                     col=list(species=c(corynebacterium="#e36255", stenotrophomonas="#ec9a86",
                                                                                        pseudomonas="#a2c5c9", klebsiella="#f3c262", 
                                                                                        acinetobacter="#f1e0ce"))),
                                    #                                     col = list(category=c(core='#16519f',accessory='#f07e74'))),
                                    # row_split = factor(labels_annotation_col[,1],levels = c("corynebacterium",'stenotrophomonas','klebsiella','pseudomonas',"acinetobacter")),
                                    # row_split = c(30,9,12,13,27),
                                    #border_color = NA,
                                    cluster_rows =as.dendrogram(dend_species_all), cluster_columns =T,
                                    # cluster_rows = T,cluster_columns =T,
                                    show_column_dend = F,show_row_dend = T,rect_gp = gpar(col= "grey"),
                                    show_column_names = T,show_row_names = T)

```{r Fig s4b}

df_args_vs_vfs <-
  read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\spearman_correlations-numberf_of_ARGs+VFs.csv)')

ggscatterstats(
  data = df_args_vs_vfs,
  x = arg_num,
  y = vf_num,
  xlab = 'Number of ARGs',
  ylab = 'Number of VFs',
  bf.message = F,results.subtitle = F
)

cor.test(df_args_vs_vfs$arg_num,df_args_vs_vfs$vf_num,
         method = 'spearman')
# Spearman's rank correlation rho
# 
# data:  df_args_vs_vfs$arg_num and df_args_vs_vfs$vf_num
# S = 13349, p-value < 2.2e-16
# alternative hypothesis: true rho is not equal to 0
# sample estimates:
#       rho 
# 0.8936982

```{r Fig s4c}

df_rgi_profile_acinetobacter = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\RGI_profile-PCoA_acinetobacter.csv)", header= TRUE)
abundance_acinetobacter = df_rgi_profile_acinetobacter[,2:(ncol(df_rgi_profile_acinetobacter)-2)]
m_abundance_acinetobacter = as.matrix(abundance_acinetobacter)
diss_acinetobacter <- vegdist(m_abundance_acinetobacter, method = "bray")

# Perform PCoA using cmdscale()
pcoa_acinetobacter <- cmdscale(diss_acinetobacter, eig = TRUE, k = 2)

#extract PCoA scores (PCoA1, PCoA2)
data_scores_acinetobacter = as.data.frame(pcoa_acinetobacter$points)
names(data_scores_acinetobacter) <- c("PCoA1", "PCoA2")

data_scores_acinetobacter$filename = df_rgi_profile_acinetobacter$filename
data_scores_acinetobacter$SamplingSite = df_rgi_profile_acinetobacter$SamplingSite

set.seed(123)
adonis2(m_abundance_acinetobacter ~ SamplingSite, data_scores_acinetobacter, method = "bray", permutations = 999)
# Permutation test for adonis under reduced model
# Terms added sequentially (first to last)
# Permutation: free
# Number of permutations: 999
# 
# adonis2(formula = m_abundance_acinetobacter ~ SamplingSite, data = data_scores_acinetobacter, permutations = 999, method = "bray")
# Df SumOfSqs      R2       F Pr(>F)
# SamplingSite  1 -0.00419 -0.0098 -0.2425  0.993
# Residual     25  0.43142  1.0098               
# Total        26  0.42724  1.0000

p_scatter_acinetobacter <- ggscatter(data_scores_acinetobacter,
                                     x = "PCoA1", 
                                     y = "PCoA2",
                                     color = 'SamplingSite',
                                     palette = c("HospitalA"="#e64833","HospitalB"="#7f59af","HospitalC"="#3e5386"),
                                     #shape = "SamplingSite",
                                     size=5,
                                     ggtheme = theme_pubr(border = T,base_size = 45),
                                     legend = 'none',
                                     ellipse = T,ellipse.level = 0.90)  + ggtitle('A. baumannii') +
  ggeasy::easy_center_title() + theme(plot.title = element_text(face = "italic",size = 45))

###-----------------------------------------------------------------------------------------------------------------------------------------

###plot RGI profile for corynebacterium based on sampling site
df_rgi_profile_corynebacterium = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\RGI_profile-PCoA_corynebacterium.csv)", header= TRUE)
abundance_corynebacterium = df_rgi_profile_corynebacterium[,2:(ncol(df_rgi_profile_corynebacterium)-2)]
m_abundance_corynebacterium = as.matrix(abundance_corynebacterium)

diss_corynebacterium <- vegdist(m_abundance_corynebacterium, method = "bray")
# Perform PCoA using cmdscale()
pcoa_corynebacterium <- cmdscale(diss_corynebacterium, eig = TRUE, k = 2)

#extract PCoA scores (PCoA1, PCoA2)
data_scores_corynebacterium = as.data.frame(pcoa_corynebacterium$points)
names(data_scores_corynebacterium) <- c("PCoA1", "PCoA2")

data_scores_corynebacterium$filename = df_rgi_profile_corynebacterium$filename
data_scores_corynebacterium$SamplingSite = df_rgi_profile_corynebacterium$SamplingSite

set.seed(123)
adonis2(m_abundance_corynebacterium ~ SamplingSite, data_scores_corynebacterium, method = "bray", permutations = 999)
# Permutation test for adonis under reduced model
# Terms added sequentially (first to last)
# Permutation: free
# Number of permutations: 999
# 
# adonis2(formula = m_abundance_corynebacterium ~ SamplingSite, data = data_scores_corynebacterium, permutations = 999, method = "bray")
# Df SumOfSqs      R2      F Pr(>F)
# SamplingSite  1  0.15791 0.05235 1.5466  0.213
# Residual     28  2.85874 0.94765              
# Total        29  3.01665 1.00000

p_scatter_corynebacterium <- ggscatter(data_scores_corynebacterium,
                                       x = "PCoA1", 
                                       y = "PCoA2",
                                       color = 'SamplingSite',
                                       palette = c("HospitalA"="#e64833","HospitalB"="#7f59af","HospitalC"="#3e5386"),
                                       #shape = "SamplingSite",
                                       size=5,
                                       ggtheme = theme_pubr(border = T,base_size = 45),
                                       legend = 'none',
                                       ellipse = T,ellipse.level = 0.90)  + ggtitle('C. striatum') +
  ggeasy::easy_center_title() + theme(plot.title = element_text(face = "italic",size = 45))

###-----------------------------------------------------------------------------------------------------------------------------------------

###plot RGI profile for klebsiella based on sampling site
df_rgi_profile_klebsiella = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\RGI_profile-PCoA_klebsiella.csv)", header= TRUE)
abundance_klebsiella = df_rgi_profile_klebsiella[,2:(ncol(df_rgi_profile_klebsiella)-2)]
m_abundance_klebsiella = as.matrix(abundance_klebsiella)

diss_klebsiella <- vegdist(m_abundance_klebsiella, method = "bray")

# Perform PCoA using cmdscale()
pcoa_klebsiella <- cmdscale(diss_klebsiella, eig = TRUE, k = 2)

#extract PCoA scores (PCoA1, PCoA2)
data_scores_klebsiella = as.data.frame(pcoa_klebsiella$points)
names(data_scores_klebsiella) <- c("PCoA1", "PCoA2")

data_scores_klebsiella$filename = df_rgi_profile_klebsiella$filename
data_scores_klebsiella$SamplingSite = df_rgi_profile_klebsiella$SamplingSite

set.seed(123)
adonis2(m_abundance_klebsiella ~ SamplingSite, data_scores_klebsiella, method = "bray", permutations = 999)
# Permutation test for adonis under reduced model
# Terms added sequentially (first to last)
# Permutation: free
# Number of permutations: 999
# 
# adonis2(formula = m_abundance_klebsiella ~ SamplingSite, data = data_scores_klebsiella, permutations = 999, method = "bray")
# Df SumOfSqs      R2      F Pr(>F)  
# SamplingSite  2  0.14675 0.40922 3.4634  0.022 *
#   Residual     10  0.21186 0.59078                
# Total        12  0.35861 1.00000

p_scatter_klebsiella <- ggscatter(data_scores_klebsiella,
                                  x = "PCoA1", 
                                  y = "PCoA2",
                                  color = 'SamplingSite',
                                  palette = c("HospitalA"="#e64833","HospitalB"="#7f59af","HospitalC"="#3e5386"),
                                  #shape = "SamplingSite",
                                  size=5,
                                  ggtheme = theme_pubr(border = T,base_size = 45),
                                  legend = 'right',
                                  ellipse = T,ellipse.level = 0.90)  + ggtitle('K. pneumoniae') +
  ggeasy::easy_center_title() + theme(plot.title = element_text(face = "italic",size = 45))

###-----------------------------------------------------------------------------------------------------------------------------------------

###plot RGI profile for pseudomonas based on sampling site
df_rgi_profile_pseudomonas = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\RGI_profile-PCoA_pseudomonas.csv)", header= TRUE)
abundance_pseudomonas = df_rgi_profile_pseudomonas[,2:(ncol(df_rgi_profile_pseudomonas)-2)]
m_abundance_pseudomonas = as.matrix(abundance_pseudomonas)

diss_pseudomonas <- vegdist(m_abundance_pseudomonas, method = "bray")

# Perform PCoA using cmdscale()
pcoa_pseudomonas <- cmdscale(diss_pseudomonas, eig = TRUE, k = 2)

#extract PCoA scores (PCoA1, PCoA2)
data_scores_pseudomonas = as.data.frame(pcoa_pseudomonas$points)
names(data_scores_pseudomonas) <- c("PCoA1", "PCoA2")

data_scores_pseudomonas$filename = df_rgi_profile_pseudomonas$filename
data_scores_pseudomonas$SamplingSite = df_rgi_profile_pseudomonas$SamplingSite

set.seed(123)
adonis2(m_abundance_pseudomonas ~ SamplingSite, data_scores_pseudomonas, method = "bray", permutations = 999)
# Permutation test for adonis under reduced model
# Terms added sequentially (first to last)
# Permutation: free
# Number of permutations: 999
# 
# adonis2(formula = m_abundance_pseudomonas ~ SamplingSite, data = data_scores_pseudomonas, permutations = 999, method = "bray")
# Df SumOfSqs     R2      F Pr(>F)
# SamplingSite  2 0.029636 0.1546 0.8229  0.657
# Residual      9 0.162059 0.8454              
# Total        11 0.191696 1.0000

p_scatter_pseudomonas <- ggscatter(data_scores_pseudomonas,
                                   x = "PCoA1", 
                                   y = "PCoA2",
                                   color = 'SamplingSite',
                                   palette = c("HospitalA"="#e64833","HospitalB"="#7f59af","HospitalC"="#3e5386"),
                                   #shape = "SamplingSite",
                                   size=5,
                                   ggtheme = theme_pubr(border = T,base_size = 45),
                                   legend = 'none',
                                   ellipse = T,ellipse.level = 0.90)  + ggtitle('P. aeruginosa') +
  ggeasy::easy_center_title() + theme(plot.title = element_text(face = "italic",size = 45))

###-----------------------------------------------------------------------------------------------------------------------------------------

###plot RGI profile for stenotrophomonas based on sampling site
df_rgi_profile_stenotrophomonas = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\RGI_profile-PCoA_stenotrophomonas.csv)", header= TRUE)
abundance_stenotrophomonas = df_rgi_profile_stenotrophomonas[,2:(ncol(df_rgi_profile_stenotrophomonas)-2)]
m_abundance_stenotrophomonas = as.matrix(abundance_stenotrophomonas)

diss_stenotrophomonas <- vegdist(m_abundance_stenotrophomonas, method = "bray")

# Perform PCoA using cmdscale()
pcoa_stenotrophomonas <- cmdscale(diss_stenotrophomonas, eig = TRUE, k = 2)

#extract PCoA scores (PCoA1, PCoA2)
data_scores_stenotrophomonas = as.data.frame(pcoa_stenotrophomonas$points)
names(data_scores_stenotrophomonas) <- c("PCoA1", "PCoA2")

data_scores_stenotrophomonas$filename = df_rgi_profile_stenotrophomonas$filename
data_scores_stenotrophomonas$SamplingSite = df_rgi_profile_stenotrophomonas$SamplingSite

set.seed(123)
adonis2(m_abundance_stenotrophomonas ~ SamplingSite, data_scores_stenotrophomonas, method = "bray", permutations = 999)
# Permutation test for adonis under reduced model
# Terms added sequentially (first to last)
# Permutation: free
# Number of permutations: 999
# 
# adonis2(formula = m_abundance_stenotrophomonas ~ SamplingSite, data = data_scores_stenotrophomonas, permutations = 999, method = "bray")
# Df SumOfSqs      R2      F Pr(>F)
# SamplingSite  1  0.11071 0.15611 1.2949  0.263
# Residual      7  0.59850 0.84389              
# Total         8  0.70922 1.00000

p_scatter_stenotrophomonas <- ggscatter(data_scores_stenotrophomonas,
                                        x = "PCoA1", 
                                        y = "PCoA2",
                                        color = 'SamplingSite',
                                        palette = c("HospitalA"="#e64833","HospitalB"="#7f59af","HospitalC"="#3e5386"),
                                        #shape = "SamplingSite",
                                        size=5,
                                        ggtheme = theme_pubr(border = T,base_size = 45),
                                        legend = 'none',
                                        ellipse = T,ellipse.level = 0.90)  + ggtitle('S. maltophilia') +
  ggeasy::easy_center_title() + theme(plot.title = element_text(face = "italic",size = 45))

(p_scatter_acinetobacter|p_scatter_corynebacterium|p_scatter_klebsiella|p_scatter_pseudomonas|p_scatter_stenotrophomonas)

```{r Fig s4d}

df_vfdb_profile_acinetobacter = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\vfdb_profile-PCoA_acinetobacter.csv)", header= TRUE)
abundance_acinetobacter = df_vfdb_profile_acinetobacter[,2:(ncol(df_vfdb_profile_acinetobacter)-2)]
m_abundance_acinetobacter = as.matrix(abundance_acinetobacter)
